---
title: "Investigate Missing Data"
author: "George"
date: "2022-10-18"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
```

## NDAR Words & Sentences Data

```{r load-and-summarize-ws-data}
data_AS_WS <- read.delim("data/ASD CDI data/mci_sentences02.txt", 
                         header = TRUE, sep = "\t", dec = ".")

# extracting first row as a descriptive dataframe
description_WS <- data_AS_WS[1:1,]
description_WS <- as.data.frame(t(description_WS))
names(description_WS) <- "description"

# what we get rid of:
eliminated_WS <- data_AS_WS %>%
  dplyr::select(c(701:709,780:850)) %>%
  slice(1:1) %>%
  gather(key = "Column names", value = "Description")#%>%
  #head(10)

# grammar items (past tense, future, not present, etc.)
#description_WS[701:709,]
# complexity and examples (e.g. longest sentences)
#description_WS[780:850,]

#using mci_sentences02_id	as a distinctive id and The NDAR Global Unique Identifier 
data_raw_AS_WS <- data_AS_WS %>%
  dplyr::select(c("mci_sentences02_id","subjectkey","interview_age", 
                  "collection_id", "dataset_id", "interview_date", 
                  "src_subject_id", "sex", 21:779)) %>% # starting from 785 is complexity. we kept vocabs, word endings, word forms.
  dplyr::select(-(689:697))
  #dplyr::select(-(684:692)) # before adding interview_age -> sex...

colnames(data_raw_AS_WS) <- as.character(unlist(data_raw_AS_WS[1,])) #unlist the row
data_raw_AS_WS = data_raw_AS_WS[-1, ]

data_raw_AS_WS <- data_raw_AS_WS %>%
  rename(id = "mci_sentences02_id",
         GUID = "The NDAR Global Unique Identifier (GUID) for research subject", 
         age = "Age in months at the time of the interview/test/sampling/imaging.",
         test_date = "Date on which the interview/genetic test/sampling/imaging/biospecimen was completed. MM/DD/YYYY",
         src_subject_id = "Subject ID how it's defined in lab/project",
         sex = "Sex of the subject") %>%
  mutate(age = as.numeric(as.character(age)))
```

Loaded data from `r nrow(data_AS_WS)` subjects.
Which of these have mcs_vc_total=="999"? 
(A code often used in SPSS for missing data.)

```{r nines}
# is any of the "missing" mcs_vc_total data salvageable?
nnn <- subset(data_AS_WS, mcs_vc_total=="999")
nnn %>% group_by(collection_id) %>% 
  summarise(n = n()) %>%
  kable()
# a lot of kids from collections 2024, 6, and 8
# 2024 2368 2666    6    8 
#  425   16    8   71   92 
```

## Item-level data

But many of these actually have at least some item-level data:
`r nrow(subset(nnn, mcs_vc1_4_grr!=""))` subjects with non-empty responses (0, 1, or 2) for 'grr'.
`r nrow(subset(nnn, mcs_vc2_16duck!=""))` subjects with non-empty responses (0, 1, or 2) for 'grr'.
`r nrow(subset(nnn, mcs_vc2_36sheep!=""))` subjects with non-empty responses (0, 1, or 2) for 'grr'.
`r nrow(subset(nnn, mcs_vc5_21drink!=""))` subjects with non-empty responses (0, 1, or 2) for 'grr'.

At least 62 subjects in collection 2024 and 4 subjects in collection 2368 have item-level data for many of the items.
[Collection 2024](https://nda.nih.gov/edit_collection.html?id=2024)'s PI is Athena Vouloumanos, and actual enrollment is listed as 209.
Indeed, there do seem to be redundant rows in our data. 
Out of the `r nrow(nnn)` entries with mcs_vc_total=="999", there are only `r length(unique(nnn$subjectkey))` unique subjectkey values, and `r length(unique(nnn$src_subject_id))` unique src_subject_id entries.
(`r nrow(nnn %>% distinct(subjectkey, interview_age))` distinct subjectkey x interview_age, so mostly not longitudinal data...)

[Collection 2368](https://nda.nih.gov/edit_collection.html?id=2368)'s PI is Susan Swedo, and reported submitting 125 CDI:WS subjects (and 114 CDI:WG).


```{r}
#duplicated(nnn[,100:700])
data_raw_AS_WS %>% 
  distinct(collection_id, id, GUID, age) %>%
  group_by(collection_id) %>%
  summarise(n=n()) %>%
  arrange(n) %>%
  kable()
```

There are 3210 subjects in collection 2024 (Vouloumanos)...is that possible?
5 experiments are listed, Shared Data tab doesn't even mention the CDI, and Data Expected tab only lists 100 Targeted Enrollment for the CDI (shows 0 Subjects Shared).
There are 17 listed publications, but their abstracts don't have Ns.

# NDAR Words & Gestures Data

```{r}
data_AS_WG <- read.delim("data/ASD CDI data/mci_words_gestures01.txt", 
                         header = TRUE, sep = "\t", dec = ".") 

# extracting first row as a descriptive dataframe
description_WG <- data_AS_WG[1:1,]
description_WG <- as.data.frame(t(description_WG))
names(description_WG) <- "description"

# we only kept vocab 
eliminated_WG <- data_AS_WG %>%
  dplyr::select(c(23:58,454:520))

#using mci_words_gestures01_id as a distinctive id and The NDAR Global Unique Identifier 

data_raw_AS_WG <- data_AS_WG %>%
  dplyr::select(c("collection_id","dataset_id","sex","mci_words_gestures01_id","subjectkey","interview_age", 59:453, 517))

colnames(data_raw_AS_WG) <- as.character(unlist(data_raw_AS_WG[1,])) #unlist the row
data_raw_AS_WG = data_raw_AS_WG[-1, ]

# what are the duplicated
AS_WG_duplicated <- data_raw_AS_WG[duplicated(colnames(data_raw_AS_WG))] # can call colnames 

# making column names unique
names(data_raw_AS_WG) <- make.unique(names(data_raw_AS_WG), sep="_")


data_raw_AS_WG <- data_raw_AS_WG %>%
  rename(id = "mci_words_gestures01_id",
         GUID = "The NDAR Global Unique Identifier (GUID) for research subject", 
         age = "Age in months at the time of the interview/test/sampling/imaging.",
         house = "MacArthur Words and Gestures: Vocabulary Checklist: House",
         sex = "Sex of the subject") %>%
  mutate(age = as.numeric(as.character(age)))


nnn_wg <- subset(data_AS_WG, mcg_vc_totcom=="999")
```

There aren't any "999"s in mcg_vc_totcom, at least.
But there are a lot entries with no item-level data

```{r}
# sum(duplicated(data_AS_WG[,59:517])) # just the vocab columns
# 7089 -- but are all of these just empty?
data_AS_WG$empty_voc_resp = rowSums(data_AS_WG[,59:517]=="")==459

novoc <- data_AS_WG %>% filter(empty_voc_resp)
```

`r nrow(novoc)` subjects are entirely blank in their vocabulary columns.
Below we show the number of subjects with blank vocabulary along with the total N per collection.

```{r}
blank_n <- novoc %>%
  group_by(collection_id) %>%
  summarise(blank_voc_n = n()) 

data_raw_AS_WG %>% 
  distinct(collection_id, id, GUID, age) %>%
  group_by(collection_id) %>%
  summarise(total_n=n()) %>%
  left_join(blank_n) %>%
  arrange(total_n) %>%
  kable()
```



