---
title: "Prep data"
author: "ASD CDI team"
date: '2022-07-19'
output: html_document
---


```{r}
library(tidyverse)
library(magrittr)
library(knitr)
```

This Rmd produces cached data files.


# Load Typically-Developing Data


```{r load-wordbank-data, eval=FALSE}
# CDI:WS
base::load("data/eng_ws_raw_data.Rds")

data_TD_WS <- eng_ws %>%
  mutate(produces = value == "produces") %>%
  filter(!is.na(category)) %>% 
  dplyr::select(data_id, produces, age, production, sex, 
                ethnicity, mom_ed, category, definition) %>%
  mutate(form="WS")

save(data_TD_WS, file="data/TD_WS.Rdata")
```


## Clean ASD CDI:WS data

Lots of data munging

```{r clean-asd-ws, eval=FALSE}
data_AS_WS <- read.delim("data/ASD CDI data/mci_sentences02.txt", 
                         header = TRUE, sep = "\t", dec = ".") %>% 
  filter(mcs_vc_total != "999")

# extracting first row as a descriptive dataframe
description_WS <- data_AS_WS[1:1,]
description_WS <- as.data.frame(t(description_WS))
names(description_WS) <- "description"


# what we get rid of:
eliminated_WS <- data_AS_WS %>%
  dplyr::select(c(701:709,780:850)) %>%
  slice(1:1) %>%
  gather(key = "Column names", value = "Description")#%>%
  #head(10)

# grammar items (past tense, future, not present, etc.)
description_WS[701:709,]
# complexity and examples (e.g. longest sentences)
description_WS[780:850,]

#using mci_sentences02_id	as a distinctive id and The NDAR Global Unique Identifier 
data_raw_AS_WS <- data_AS_WS %>%
  dplyr::select(c("mci_sentences02_id","subjectkey","interview_age", 
                  "collection_id", "dataset_id", "interview_date", 
                  "src_subject_id", "sex", 21:779)) %>% # starting from 785 is complexity. we kept vocabs, word endings, word forms.
  dplyr::select(-(689:697))
  #dplyr::select(-(684:692)) # before adding interview_age -> sex...

colnames(data_raw_AS_WS) <- as.character(unlist(data_raw_AS_WS[1,])) #unlist the row
data_raw_AS_WS = data_raw_AS_WS[-1, ]

data_raw_AS_WS <- data_raw_AS_WS %>%
  rename(id = "mci_sentences02_id",
         GUID = "The NDAR Global Unique Identifier (GUID) for research subject", 
         age = "Age in months at the time of the interview/test/sampling/imaging.",
         test_date = "Date on which the interview/genetic test/sampling/imaging/biospecimen was completed. MM/DD/YYYY",
         src_subject_id = "Subject ID how it's defined in lab/project",
         sex = "Sex of the subject") %>%
  mutate(age = as.numeric(as.character(age)))

data_clean_AS_WS <- data_raw_AS_WS %>%
  gather(key = "definition", value = "value", 
         -c(id,GUID,age,collection_id,dataset_id,test_date,src_subject_id,sex)) %>%
  separate(definition, c("category","definition"),sep = "\\. ") %>%
  mutate_all(na_if,"",)%>% #if blank then fill in NA
   mutate(value = ifelse(value == 0, FALSE, TRUE))

data_all_AS_WS <- data_clean_AS_WS %>%
     group_by(category, definition, age) %>%
       summarise(num_true = sum(value, na.rm = TRUE),
                 num_false = n() - num_true,
                 prop = num_true/n())

# unique(data_all_AS_WS$category)

data_clean_AS_WS <- data_clean_AS_WS %>% filter(category!="Word forms, noun", 
                                                category!="Word forms, verbs",
                                                category!="Word endings, nouns",
                                                category!="Word endings, verbs") %>%
  mutate(category = case_when(category=="Sound Effects and Animal Sounds" ~ "sounds",
                              category=="Animals (Real or Toy)" ~ "animals",
                              category=="Vehicles (Real or Toy)" ~ "vehicles",
                              category=="Food and Drink" ~ "food_drink",
                              category=="Clothinq" ~ "clothing",
                              category=="Body Parts" ~ "body_parts",
                              category=="Small Household Items" ~ "household",
                              category=="Furniture and Rooms" ~ "furniture_rooms",
                              category=="Outside Thlnqs" ~ "outside",
                              category=="Action Words" ~ "action_words",
                              category=="Places to Go" ~ "places",
                              category=="Helping Verbs" ~ "helping_verbs",
                              category=="Connectinq Words" ~ "connecting_words",
                              category=="Descriptive Words" ~ "descriptive_words",
                              category=="Words About Time" ~ "time_words",
                              category=="Quantifiers and Articles" ~ "quantifiers",
                              category=="Games and Routines" ~ "games_routines",
                              category=="Question Words" ~ "question_words",
                              category=="Prepositions and Locations" ~ "locations",
                              category=="Helpinq Verbs" ~ "helping_verbs",
                              TRUE ~ category)) %>%
  mutate(category = tolower(category), 
         definition = case_when(definition=="baa" ~ "baa baa",
                                definition=="cockadoodle" ~ "cockadoodledoo",
                                definition=="quack" ~ "quack quack",
                                definition=="uhoh" ~ "uh oh",
                                definition=="woof" ~ "woof woof",
                                definition=="yum" ~ "yum yum",
                                definition=="chicken" & category=="food_drink" ~ "chicken (food)",
                                definition=="chicken" ~ "chicken (animal)",
                                definition=="fish" & category=="food_drink" ~ "fish (food)",
                                definition=="fish" ~ "fish (animal)",
                                definition=="playdough" ~ "play dough",
                                definition=="vagina" ~ "vagina*",
                                definition=="penis" ~ "penis*",
                                definition=="frenchfries" ~ "french fries",
                                definition=="greenbeans" ~ "green beans",
                                definition=="toy" ~ "toy (object)",
                                definition=="drink" & category=="action_words" ~ "drink (action)",
                                definition=="drink" ~ "drink (beverage)",
                                definition=="gasstation" ~ "gas station",
                                definition=="orange" & category=="food_drink" ~ "orange (food)",
                                definition=="orange" ~ "orange (description)",
                                definition=="allgone" ~ "all gone",
                                definition=="water" & category=="food_drink" ~ "water (beverage)",
                                definition=="water" ~ "water (not beverage)",
                                definition=="feet" ~ "foot",
                                definition=="callph" ~ "call (on phone)",
                                definition=="clean" & category=="action_words" ~ "clean (action)",
                                definition=="clean" ~ "clean (description)",
                                definition=="owie  booboo" ~ "owie/boo boo",
                                definition=="dont" ~ "don't",
                                definition=="5bowl" ~ "bowl",
                                definition=="can" & category=="household" ~ "can (object)",
                                definition=="can" & category=="helping_verbs" ~ "can (auxiliary)",
                                definition=="rockingchair" ~ "rocking chair",
                                definition=="alot" ~ "a lot",
                                definition=="buttocks/bottom" ~ "buttocks/bottom*",
                                definition=="daddy" ~ "daddy*",
                                definition=="childname" ~ "child's own name",
                                definition=="washingmachine" ~ "washing machine",
                                definition=="try" ~ "try/try to",
                                definition=="work" & category=="places" ~ "work (place)",
                                definition=="work" ~ "work (action)",
                                definition=="giveme five" ~ "give me five!",
                                definition=="mommy" ~ "mommy*",
                                definition=="grandma" ~ "grandma*",
                                definition=="church" ~ "church*",
                                definition=="daddy" ~ "daddy*",
                                definition=="grandpa" ~ "grandpa*",
                                definition=="patty cake" ~ "pattycake",
                                definition=="dry" & category=="action_words" ~ "dry (action)",
                                definition=="dry" ~ "dry (description)",
                                definition=="lemme" ~ "lemme/let me",
                                definition=="tissklee" ~ "tissue/kleenex",
                                definition=="did" ~ "did/did ya",
                                definition=="gonna get  you" ~ "gonna get you!",
                                definition=="peanutbutter" ~ "peanut butter",
                                definition=="playpen" ~ "play pen",
                                definition=="potatochip" ~ "potato chip",
                                definition=="wanna" ~ "wanna/want to",
                                definition=="watch" & category=="action_words" ~ "watch (action)",
                                definition=="watch" ~ "watch (object)",
                                definition=="dress" ~ "dress (object)",
                                definition=="gonna" ~ "gonna/going to",
                                definition=="gotta" ~ "gotta/got to",
                                definition=="hafta" ~ "hafta/have to",
                                definition=="highchair" ~ "high chair",
                                definition=="lawnmower" ~ "lawn mower",
                                definition=="little" ~ "little (description)",
                                definition=="petname" ~ "pet's name",
                                definition=="so big" ~ "so big!",
                                definition=="need" ~ "need/need to",
                                definition=="shush" ~ "shh/shush/hush",
                                definition=="swing" & category=="action_words" ~ "swing (action)",
                                definition=="swing" ~ "swing (object)",
                                definition=="slide" & category=="action_words" ~ "slide (action)",
                                definition=="slide" ~ "slide (object)",
                                TRUE ~ definition))

save(data_clean_AS_WS, file="data/ASD_WS.Rdata")
# summary(data_all_AS_WS)
```


## Clean ASD CDI:WG data

Note: found a problem in the NDAR description file -- mcg_vc18_back is given the definition "backyard" (making a duplicate) instead of "back".
Also, "throw" (col 517) was left out of previous semantic network growth analyses.

```{r clean-asd-wg, eval=FALSE}
data_AS_WG <- read.delim("data/ASD CDI data/mci_words_gestures01.txt", 
                         header = TRUE, sep = "\t", dec = ".") %>% 
  filter(mcg_vc_totcom != "999")

# extracting first row as a descriptive dataframe
description_WG <- data_AS_WG[1:1,]
description_WG <- as.data.frame(t(description_WG))
names(description_WG) <- "description"

# we only kept vocab 
eliminated_WG <- data_AS_WG %>%
  dplyr::select(c(23:58,454:520))

#using mci_words_gestures01_id as a distinctive id and The NDAR Global Unique Identifier 

data_raw_AS_WG <- data_AS_WG %>%
  dplyr::select(c("collection_id","dataset_id","sex","mci_words_gestures01_id","subjectkey","interview_age", 59:453, 517))

colnames(data_raw_AS_WG) <- as.character(unlist(data_raw_AS_WG[1,])) #unlist the row
data_raw_AS_WG = data_raw_AS_WG[-1, ]

# what are the duplicated
AS_WG_duplicated <- data_raw_AS_WG[duplicated(colnames(data_raw_AS_WG))] # can call colnames 

# making column names unique
names(data_raw_AS_WG) <- make.unique(names(data_raw_AS_WG), sep="_")


data_raw_AS_WG <- data_raw_AS_WG %>%
  rename(id = "mci_words_gestures01_id",
         GUID = "The NDAR Global Unique Identifier (GUID) for research subject", 
         age = "Age in months at the time of the interview/test/sampling/imaging.",
         house = "MacArthur Words and Gestures: Vocabulary Checklist: House",
         sex = "Sex of the subject") %>%
  mutate(age = as.numeric(as.character(age)))


data_clean_AS_WG <- data_raw_AS_WG %>%
  gather(key = "definition", value = "value", 
         -c(id,GUID,age,sex,dataset_id,collection_id)) %>%
  #separate(definition, c("category","definition"),sep = "\\. ") %>%
  mutate_all(na_if,"",) %>% #if blank then fill in NA
   mutate(value = ifelse(value == 0, FALSE, TRUE))

data_all_AS_WG <- data_clean_AS_WG %>%
     group_by(definition, age) %>%
       summarise(num_true = sum(value, na.rm = TRUE),
                 num_false = n() - num_true,
                 prop = num_true/n())

data_clean_AS_WG <- data_clean_AS_WG %>% 
  mutate(definition = case_when(
    definition=="bye or bye bye" ~ "bye",
    definition=="chicken" ~ "chicken (animal)",
    definition=="chicken_1" ~ "chicken (food)",
    definition=="peek-a-boo" ~ "peekaboo",
    definition=="water" ~ "water (beverage)",
    definition=="water_1" ~ "water (not beverage)",
    definition=="church" ~ "church*",
    definition=="clean" ~ "clean (action)",
    definition=="clean_1" ~ "clean (description)",
    definition=="daddy" ~ "daddy*",
    definition=="dress" ~ "dress (object)",
    definition=="towl" ~ "towel",
    definition=="grandpa" ~ "grandpa*",
    definition=="grandma" ~ "grandma*",
    definition=="mommy" ~ "mommy*",
    definition=="owie/ boo boo" ~ "owie/boo boo",
    definition=="little" ~ "little (description)",
    definition=="drink" ~ "drink (beverage)",
    definition=="drink_1" ~ "drink (action)",
    definition=="dry" ~ "dry (description)",
    definition=="fire truck" ~ "firetruck",
    definition=="fish" ~ "fish (animal)",
    definition=="fish_1" ~ "fish (food)",
    definition=="toy" ~ "toy (object)",
    definition=="teddy bear" ~ "teddybear",
    definition=="swing" ~ "swing (object)",
    definition=="swing_1" ~ "swing (action)",
    definition=="work" ~ "work (place)",
    definition=="orange" ~ "orange (food)",
    definition=="patty cake" ~ "pattycake",
    definition=="slide" ~ "slide (object)",
    definition=="watch" ~ "watch (object)",
    definition=="watch_1" ~ "watch (action)",
    definition=="backyard_1" ~ "back", # "mcg_vc18_back"
    TRUE ~ definition
  ))


save(data_clean_AS_WG, file="data/ASD_WG.Rdata")

# summary(data_all_AS_WG)
```

# Merging in dataset ID information and cleaning

We need to consider which ASD studies are relevant to include (e.g., some may be from more severe cases than others), as well as which have oddities (e.g., duplicate/mismatched subject IDs).
At a first glance at the summary by dataset_id, a few of the datasets have all 0 production scores (e.g., dataset_id = c(9137, 17935, 21697, 17999, 17151)).
Are these true 0 CDI scores, or are the CDI data for these studies somehow missing?
As these studies comprise 1170 participants (of our 4488 total ASD sample), it is important to know what's going on, and whether or not they should be excluded.
I also note that studies 17935 and 21697 suspiciously have the same age range, mean_age, and number of subjects -- are these 194 subjects duplicated under different dataset_ids?

For now, I remove all of the datasets without any non-zero production scores.

```{r load-asd-data}
load("data/ASD_WS.Rdata") # data_clean_AS_WS
load("data/ASD_WG.Rdata") # data_clean_AS_WG
load("data/TD_WS.Rdata") # data_TD_WS
```


```{r}
# data_clean_AS_WS has 8 unique collection_ids, and 20 unique dataset_ids
# data_clean_AS_WG has 20 unique collection_ids, and 44 unique dataset_ids
#  -- collection_id (e.g. 2024) can be shared across multiple dataset_ids (9959, 9960, 9961) --> are these the same kids at different ages?

#asd_ws <- data_clean_AS_WS %>% group_by(id, GUID, age, sex, dataset_id) %>%
#  summarise(production = sum(value, na.rm=T))

#asd_wg <- data_clean_AS_WG %>% group_by(id, GUID, age, sex, dataset_id) %>%
#  summarise(production = sum(value, na.rm=T))

# remove extreme ages
#data_clean_AS_WS <- data_clean_AS_WS %>%
#  filter(age>=12, age<=48)

#data_clean_AS_WG <- data_clean_AS_WG %>%
#  filter(age>=8, age<=36)


data_clean_AS_WS %>% group_by(id, age, sex, dataset_id) %>%
  summarise(production = sum(value, na.rm=T)) %>%
  group_by(collection_id) %>%
  summarise(min_age = min(age), 
            max_age = max(age), 
            mean_age = mean(age),
            n = n(), 
            mean_prod = mean(production)) %>%
  arrange(desc(n))

AS_WS_summary %>%
  kable(format = "html", table.attr = "style='width:50%;'", digits=1)
```

According to the [NDA website](https://nda.nih.gov/contribute/using-the-nda-guid.html), the GUID is a unique identifier for each participant.
Thus, in the WG dataset there are `r length(unique(data_clean_AS_WG$GUID))` participants, and in the WS dataset there are `r length(unique(data_clean_AS_WS$GUID))` participants.
The much larger number of rows may represent longitudinal data, or duplicates (e.g., copies of the same participant's CDI administration across multiple datasets, or perhaps collections).

```{r identifying-duplicates}
# no complete duplicates in data_clean, and none grouped by GUID, age, and production

dim(data_clean_AS_WS %>% distinct(GUID, age, sex, dataset_id)) # 4248
dim(data_clean_AS_WS %>% distinct(id, GUID, age, sex, dataset_id)) # 4488
dim(data_clean_AS_WS %>% distinct(id, GUID, age, sex, collection_id)) # 4488

# ids are unique (i.e., administration), whereas GUID identifies a child

asd_ws <- data_clean_AS_WS %>% group_by(id, GUID, age, sex, collection_id) %>%
  summarise(production = sum(value, na.rm=T))
# 1940 with collection_id, 4248 with dataset_id, 

asd_wg <- data_clean_AS_WG %>% group_by(id, GUID, age, sex, collection_id) %>%
  summarise(production = sum(value, na.rm=T))
# 4780 without dataset_id, 4783 with collection_id, 8091 with dataset_id

#sum(duplicated(asd_wg))
#sum(duplicated(asd_ws))

#sum(duplicated(asd_ws[,c("age","sex","production","collection_id")]))
# 3450/4488 ! (1038 unique?)

#sum(duplicated(asd_wg[,c("age","sex","production","collection_id")]))
# 7003/8488 ! (1485 unique?)

# these are getting some large production scores...adding up multiple administrations??
asd_wg %>% ggplot(aes(x=age, y=production, color=sex, group=GUID)) + 
  geom_point(alpha=.2) + geom_line(alpha=.1) + # facet_wrap(. ~ collection_id) +
  theme_classic()

asd_ws %>% ggplot(aes(x=age, y=production, color=sex, group=GUID)) + 
  geom_point(alpha=.2) + geom_line(alpha=.1) + # facet_wrap(. ~ collection_id) +
  theme_classic()
```

```{r}
AS_WG_summary <- data_clean_AS_WG %>% 
  group_by(collection_id, age, sex, dataset_id) %>%
  summarise(production = sum(value, na.rm=T)) %>%
  group_by(collection_id) %>%
  summarise(min_age = min(age), 
            max_age = max(age), 
            mean_age = mean(age),
            n = n(), 
            mean_prod = mean(production)) %>%
  arrange(desc(n)) 

AS_WG_summary %>%
  kable(format = "html", table.attr = "style='width:50%;'", digits=1)
```

Remove all datasets with all 0 production.
(Some of which should certainly not have 0 production, according to their associated NDA webpages and publications, e.g. [1885](https://nda.nih.gov/edit_collection.html?id=1885), [Crandall et al. 2019](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6808365/pdf/JSLHR-62-1787.pdf))

```{r}
zero_prod_WG <- filter(AS_WG_summary, mean_prod < 1) %>% pull(collection_id)
zero_prod_WS <- filter(AS_WS_summary, mean_prod < 1) %>% pull(collection_id)

data_clean_AS_WG %<>% filter(!(collection_id %in% zero_prod_WG))
data_clean_AS_WS %<>% filter(!(collection_id %in% zero_prod_WS))
```



```{r}
data_sources <- read_csv("data/NDA data sources.csv")
data_clean_AS_WS %<>%
  mutate(collection_id = as.numeric(collection_id)) %>%
  left_join(select(data_sources, collection_id, collection_title))

data_clean_AS_WG %<>%
  mutate(collection_id = as.numeric(collection_id)) %>%
  left_join(select(data_sources, collection_id, collection_title))
```

We will constrain our analysis to those children close to the intended age ranges, extending a wider margin for older children to capture the attenuated language learning of children with ASD.

```{r}
asd_ws <- data_clean_AS_WS %>% 
  group_by(id, age, sex, dataset_id) %>%
  summarise(production = sum(value, na.rm=T))

asd_wg <- data_clean_AS_WG %>% 
  group_by(id, age) %>%
  summarise(production = sum(value, na.rm=T))
```


Note that there are many CDI:WS administrations for ASD children outside the intended age range (16-30 months): `r nrow(subset(asd_ws, age<16))` children aged <16 months (mean production = `r round(mean(subset(asd_ws, age<16)$production), 0)` words), and `r nrow(subset(asd_ws, age>30))` children aged >30 months (mean production = `r round(mean(subset(asd_ws, age>30)$production), 0)` words).

Similarly, there are many CDI:WG administrations for ASD children outside the intended age range (8-16 months): `r nrow(subset(asd_wg, age<8))` children aged <12 months (mean production = `r round(mean(subset(asd_wg, age<8)$production), 0)` words), and `r nrow(subset(asd_wg, age>16))` children aged >16 months (mean production = `r round(mean(subset(asd_wg, age>16)$production), 0)` words).

Thus, for the CDI:WS we include `r nrow(subset(asd_ws, age>=12 & age<=48))` children aged 12-48 months (removing only `r round(100*(nrow(asd_ws) - nrow(subset(asd_ws, age>=12 & age<=48)))/nrow(asd_ws),1)`% of the data).
For the CDI:WG we include `r nrow(subset(asd_wg, age>=8 & age<=36))` children aged 8-36 months (removing only `r round(100*(nrow(asd_wg) - nrow(subset(asd_wg, age>=8 & age<=36)))/nrow(asd_wg),1)`% of the data).

```{r}
data_clean_AS_WG %<>% filter(age>=8, age<=36)
data_clean_AS_WS %<>% filter(age>=12, age<=48)
```

# Final dataset stats

```{r}
data_clean_AS_WG %>% 
  group_by(collection_id, collection_title, id) %>% 
  count() %>% 
  group_by(collection_id, collection_title) %>% 
  count() %>% 
  kable()
```


```{r}
data_clean_AS_WS %>% 
  group_by(collection_id, collection_title, id) %>% 
  count() %>% 
  group_by(collection_id, collection_title) %>% 
  count() %>% 
  kable()
```

# Save data

```{r, eval=F}
d_asd_wg <- data_clean_AS_WG
d_asd_ws <- data_clean_AS_WS
d_td_ws <- data_TD_WS

save(d_asd_wg, d_asd_ws, d_td_ws,
     file = "data/cached_data.Rds")
```

