---
title: "DIF analysis"
author: "ASD CDI team"
date: '2022-07-19'
output: html_document
---


## DIF Analysis for WS data

```{r}

wb_items = d_td_ws %>% 
  distinct(category, definition)

asd_items = data_clean_AS_WS %>% 
  distinct(category, definition)

td_mat <- d_td_ws %>% dplyr::select(data_id, definition, produces) %>% 
  pivot_wider(id_cols = data_id, names_from = definition, values_from = produces)
  

asd_mat <- data_clean_AS_WS %>% rename(data_id=id) %>%
  filter(!is.element(dataset_id, bad_ws_datasets)) %>%
  dplyr::select(data_id, definition, value) %>% 
  pivot_wider(id_cols = data_id, names_from = definition, values_from = value)

demo_td <- d_td_ws %>% 
  distinct(data_id, age, production, sex, ethnicity, mom_ed) %>% 
  mutate(group = "TD")

demo_asd <- data_clean_AS_WS %>% rename(data_id=id) %>%
  filter(!is.element(dataset_id, bad_ws_datasets)) %>%
  mutate(data_id = as.numeric(data_id),
         group = "ASD") %>%
  group_by(data_id, age, group) %>%
  summarise(production = sum(value, na.rm=T)) 
```


```{r, echo=F, message=F, warning=F}

#cor.test(demo_asd$age, demo_asd$production) # .40
#cor.test(demo_td$age, demo_td$production) # .75

# no overlap in data_ids, right?
#intersect(demo_td$data_id, demo_asd$data_id) # 0 - good

bad_Ss_td = demo_td[which(demo_td$production==0),]$data_id 
bad_Ss_asd = demo_asd[which(demo_asd$production==0),]$data_id 

# combine data
d_mat <- rbind(td_mat, asd_mat) %>% filter(!is.element(data_id, c(bad_Ss_asd, bad_Ss_td)))
d_demo <- demo_td %>% dplyr::select(data_id, age, group, production) %>% 
  bind_rows(demo_asd) %>%
  filter(!is.element(data_id, c(bad_Ss_asd, bad_Ss_td)))

sids = d_mat$data_id
d_mat$data_id = NULL
d_mat = data.matrix(d_mat)
row.names(d_mat) = sids

d_group = as.character(d_demo$group)

source("helper_functions/DIF_helpers.R")


```

`r length(bad_Ss_td)` typically-developing (TD) children were removed from the wordbank data (`r nrow(demo_td)` total) due to their not yet producing any words.
`r length(bad_Ss_asd)` children with ASD were removed from the NDAR data (`r nrow(demo_asd)` total) due to their not yet producing any words.


```{r fit-ws-model, eval=F}
mod_dev_group <- fit_mod_intuitive(d_mat, d_group)

save(mod_dev_group, file="data/prodWS_IRT_model.Rds")
```

```{r load-ws-model}
load("data/prodWS_IRT_model.Rds") # 12-48 mos ASD
#plot_glimmer(mod_dev_group, colnames(d_mat), colnames(d_mat), 
#             plotName="GLIMMER_asd_prodWS_age12-48mos")

#load("data/prodWS_IRT_model_16-48mos.Rds")
#plot_glimmer(mod_dev_group, colnames(d_mat), colnames(d_mat), 
#             plotName="GLIMMER_asd_prodWS_age16-48mos")
# doesn't make a difference whether we exclude 12-15 month-old ASD kids or not


mm_asd <- extract_group_df(mod_dev_group, groups=c("TD","ASD"))
#dif_hist <- item_difficulty_difference_histogram(mm_asd)

thresh = median(mm_asd$d_diff_abs) + 2*sd(mm_asd$d_diff_abs)
big_dif = mm_asd[which(mm_asd$d_diff_abs > thresh),]

dif_histn <- item_difficulty_difference_histogram(mm_asd, withNormal = T)
print(dif_histn)
```

The majority of items are easier for TD than for ASD children. 
We examine the extrema: items with an absolute difficulty difference of at least 2 standard deviations (|d_diff| = `r round(thresh,2)`; red dotted lines in histogram).
These `r nrow(big_dif)` extrema are listed below.

```{r}
big_dif <- big_dif %>% left_join(wb_items)

big_dif %>% arrange(d_diff) %>% 
  relocate(category, definition) %>%
  rename(d_TD=d_g1, d_ASD=d_g2) %>%
  dplyr::select(-a1, -group1, -group2) %>%
  kable(format = "html", table.attr = "style='width:50%;'", digits=2)
```

```{r}
sort(table(big_dif$category)) %>% kable(col.names=c("Category","Frequency"))
```

Mostly people and action words.

## Ability vs. Sumscore by Age

```{r, eval=F, echo=F}
d_demo <- d_demo %>% 
  left_join(tibble(data_id = rownames(d_mat), 
                   ability = fscores(mod_dev_group, method = "MAP")[,1]))
# MAP: Warning: The following factor score estimates failed to converge successfully:
#  2448,2750
```



# CDI:WG Production

### Examine ASD WG datasets

```{r}
data_clean_AS_WG %>% group_by(id, age, sex, dataset_id) %>%
  summarise(comprehension = sum(value, na.rm=T)) %>%
  group_by(dataset_id) %>%
  summarise(min_age = min(age), max_age = max(age), mean_age = mean(age),
            n = n(), mean_comp = mean(comprehension)) %>%
  arrange(desc(n)) %>%
  kable(format = "html", table.attr = "style='width:50%;'", digits=1)
```

Datasets with all 0 comprehension scores: c(12095, 9138, 10754, 11574, 8703, 8667, 18066, 14458, 17999, 12942, 11717, 8368, 17935, 8176, 8370, 8535, 9507, 12891, 12820, 12790, 8532, 8912, 8922)
10754 and 11574 have identical age ranges, mean ages, and Ns, as do 8176 and 8370.
16641 and 14747 have identical age ranges, mean ages, Ns, and average comprehension scores.
After removing all of the 0-comprehension datasets, there are only 3829 participants.

```{r}
bad_asd_wg_datasets = c(12095, 9138, 10754, 11574, 8703, 8667, 18066, 14458, 17999, 12942, 11717, 8368, 17935, 8176, 8370, 8535, 9507, 12891, 12820, 12790, 8532, 8912, 8922)
data_clean_AS_WG <- data_clean_AS_WG %>% filter(!is.element(dataset_id, bad_asd_wg_datasets))
```


```{r, echo=F}
base::load("data/eng_wg_raw_data.Rds")

d_wg <- eng_wg %>%
  mutate(produces = value == "produces") %>%
  filter(!is.na(category)) %>% 
  dplyr::select(data_id, produces, age, production, sex, ethnicity, mom_ed, category, definition) %>%
  mutate(form="WG")

wg_items = d_wg %>% distinct(category, definition)

asd_items = data_clean_AS_WG %>% distinct(definition) # category not present

# match ASD and wordbank defs:
#intersect(wg_items$definition, asd_items$definition) # 396/396
#sort(setdiff(wg_items$definition, asd_items$definition))
#sort(setdiff(asd_items$definition, wg_items$definition)) 

td_mat_wg <- d_wg %>% dplyr::select(data_id, definition, produces) %>% 
  pivot_wider(id_cols = data_id, names_from = definition, values_from = produces)
  

asd_mat_wg <- data_clean_AS_WG %>% rename(data_id=id) %>%
  dplyr::select(data_id, definition, value) %>% 
  pivot_wider(id_cols = data_id, names_from = definition, values_from = value) %>%
  relocate("throw", .after="take")

# same order?
# names(td_mat_wg)==names(asd_mat_wg)

demo_td_wg <- d_wg %>% distinct(data_id, age, production, sex, ethnicity, mom_ed) %>% 
  mutate(group = "TD")
demo_asd_wg <- data_clean_AS_WG %>% rename(data_id=id) %>%
  mutate(data_id = as.numeric(data_id),
         group = "ASD") %>%
  group_by(data_id, age, group) %>%
  summarise(production = sum(value, na.rm=T)) 


# no overlap in data_ids, right?
#intersect(demo_td_wg$data_id, demo_asd_wg$data_id) # 0 - good

bad_Ss_td = demo_td_wg[which(demo_td_wg$production==0),]$data_id # 241
bad_Ss_asd = demo_asd_wg[which(demo_asd_wg$production==0),]$data_id # 5363

# combine data
d_mat_wg <- rbind(td_mat_wg, asd_mat_wg) %>% filter(!is.element(data_id, c(bad_Ss_asd, bad_Ss_td)))
d_demo_wg <- demo_td_wg %>% dplyr::select(data_id, age, group, production) %>% 
  bind_rows(demo_asd_wg) %>%
  filter(!is.element(data_id, c(bad_Ss_asd, bad_Ss_td)))

sids = d_mat_wg$data_id
d_mat_wg$data_id = NULL
d_mat_wg = data.matrix(d_mat_wg)
row.names(d_mat_wg) = sids

d_group = as.character(d_demo_wg$group)

```

`r length(bad_Ss_td)` typically-developing (TD) children were removed from the wordbank data (`r nrow(demo_td)` total) due to their not yet producing any words.
`r length(bad_Ss_asd)` children with ASD were removed from the NDAR data (`r nrow(demo_asd)` total) due to their not yet producing any words.

```{r, echo=F, results=F, message=F, fig.cap="Production sumscores on the CDI:WG for TD vs. ASD children."}
# Let's show ASD and TD separately

demo_td_wg <- demo_td_wg %>% mutate(prop_produced = production / 396) %>%
   mutate(prop_produced = case_when(prop_produced == 0 ~ 0.001,
                                    prop_produced == 1 ~ 0.999,
                                    TRUE ~ prop_produced)) %>% # can't have 1 or 0
   dplyr::select(-sex, -ethnicity, -mom_ed)

demo_asd_wg <- demo_asd_wg %>% mutate(prop_produced = production / 396) %>%
   mutate(prop_produced = case_when(prop_produced == 0 ~ 0.001,
                                    prop_produced == 1 ~ 0.999,
                                    TRUE ~ prop_produced)) # can't have 1 or 0

gam_mod_td <- gamlss(prop_produced ~ pbm(age, lambda = 10000),
                 sigma.formula = ~ pbm(age, lambda = 10000),
                 family = BE, data = demo_td_wg)

gam_mod_asd <- gamlss(prop_produced ~ pbm(age, lambda = 10000),
                 sigma.formula = ~ pbm(age, lambda = 10000),
                 family = BE, data = demo_asd_wg)

cents_asd_wg <- centiles.pred(gam_mod_asd, cent = c(90, 75, 50, 25, 10),
                       xname = "age", xvalues = 8:48) %>%
  tibble() %>% pivot_longer(2:6, names_to = "percentile", values_to = "pred") %>%
  rename(age=x)


cents_td_wg <- centiles.pred(gam_mod_td, cent = c(90, 75, 50, 25, 10),
                       xname = "age", xvalues = 8:24) %>%
  tibble() %>% pivot_longer(2:6, names_to = "percentile", values_to = "pred") %>%
  rename(age=x)

p1 <- ggplot(data=demo_td_wg, aes(x=jitter(age))) +
  geom_point(data=demo_td_wg, alpha=.1, aes(y=production)) + 
  geom_line(data=cents_td_wg, aes(x=age, y=pred * 396, linetype = percentile)) + 
  theme_classic() + xlab("Age (months)") + ylab("Production Sumscore") +
  ggtitle("Typically-Developing")

p2 <- ggplot(data=demo_asd_wg %>% filter(age<60), aes(x=jitter(age))) +
  geom_point(data=demo_asd_wg %>% filter(age<60), alpha=.1, aes(y=production)) + 
  geom_line(data=cents_asd_wg, aes(x=age, y=pred * 396, linetype = percentile)) + 
  theme_classic() + xlab("Age (months)") + ylab("Production Sumscore") + 
  ggtitle("ASD")

ggpubr::ggarrange(p1, p2, ncol=2, common.legend = T)
```

```{r fit-wg-model, eval=F}
mod_dev_group <- fit_mod_intuitive(d_mat_wg, d_group)
save(mod_dev_group, file="data/prodWG_IRT_model.Rds")
```

```{r load-wg-model}
load("data/prodWG_IRT_model.Rds") # 8-36mo ASD
#plot_glimmer(mod_dev_group, colnames(d_mat_wg), colnames(d_mat_wg), 
#             plotName="GLIMMER_asd_prodWG_age8-36mos")


mm_asd_wg <- extract_group_df(mod_dev_group, groups=c("TD","ASD"))
#dif_hist <- item_difficulty_difference_histogram(mm_asd)

thresh_wg = median(mm_asd_wg$d_diff_abs) + 2*sd(mm_asd_wg$d_diff_abs)
big_dif_wg = mm_asd_wg[which(mm_asd_wg$d_diff_abs > thresh_wg),]

dif_histn_wg <- item_difficulty_difference_histogram(mm_asd_wg, withNormal = T)
print(dif_histn_wg)
```

The majority of the items are much easier for TD than for ASD children. 
We examine the extrema: items with an absolute difficulty difference of at least 2 standard deviations (|d_diff| = `r round(thresh_wg,2)`; red dotted lines in histogram).
These `r nrow(big_dif_wg)` extrema are listed below.

```{r}
big_dif_wg <- big_dif_wg %>% left_join(wg_items)

big_dif_wg %>% arrange(d_diff) %>% 
  relocate(category, definition) %>%
  rename(d_TD=d_g1, d_ASD=d_g2) %>%
  dplyr::select(-a1, -group1, -group2) %>%
  kable(format = "html", table.attr = "style='width:50%;'", digits=2)
```
